Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits

### 2022-11-10 04_paper/1110_draft.Rmd
updates to hypotheses, results, and conclusion

# Hypotheses [just a start]

@@

However, as noted in the discussion of China's overseas financing, prior research points to the importance of distinguishing between Beijing's ODA-like (aid) activities and its OOF-like (debt) activities. Both coverage and visits are visible activities that help to complement the material resources provided in the form of aid. However, as noted previously, debt tends to be associated with more market-based goals, which have historically been controversial in the development community. This leads to the reasonable conclusion that aid, rather than debt, should have closer correspondence with coverage and visits than debt.

To the extent that aid supports Beijing's foreign policy goals, we should expect that aid recipients will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.

@@

Conversely, to the extent that loans function in service of market-based objectives rather than political ones, then countries that owe greater debt to Beijing also will not necessarily be more likely targets of greater foreign-facing media coverage in *Xinhua* nor more likely hosts of a greater number of diplomatic missions from Beijing.

@@

Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the four regression specifications enumerated in the methods discussion. The figure contains a left and right panel. On the right, results are shown for models 1 and 2 while on the left, results are shown for models 3 and 4. Recall that the first pair of models uses continuous measures of aid and debt as predictors while the second pair uses binary indicators of whether a developing country is an aid recipient, a debtor, or both of Beijing's. Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor). The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate. Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits. Zero is indicated along the x-axis via a vertical dotted line. If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.

@@

To put these estimates in more substantive terms, it will be helpful to show some computed marginal effects. Table \@ref(tab:mareff) shows the predicted change in each of the outcomes given a percent increase in either aid or debt in Pakistan in 2017. Cell entries in the first column denote the \% change in the number of times Pakistan appears in *Xinhua* in 2017 while entries in the second column denote the \% change in the number of times Pakistan hosts diplomatic missions from Beijing in 2017. The first row indicates what this change is per a hypothetical percent increase aid from China to Pakistan, and the second row indicates what this change is per a hypothetical percent increase in loans (debt) from China to Pakistan. The marginal effect for aid on coverage in this case is 0.76\% while the marginal effect for debt on visits is 0.05\%.

>>>>

# Hypotheses

@@

To test this logic, we examine the extent to which recipients of Chinese overseas development financing also receive disproportionate coverage in *Xinhua* and host a disproportionate number of diplomatic missions from Beijing. We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships. As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its comercial goals. We therefore should expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.

In particular, to the extent that aid supports Beijing's foreign policy goals, we should expect that aid recipients will be both targets of greater foreign-facing media coverage in *Xinhua* and hosts of a greater number of diplomatic missions from Beijing.

@@

Conversely, to the extent that loans function in service of market-based objectives rather than political ones, countries that owe greater debt to Beijing also will not necessarily be more likely targets of greater foreign-facing media coverage in *Xinhua* nor more likely hosts of a greater number of diplomatic missions from Beijing.

@@

Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the two regression specifications enumerated in the methods discussion. Recall that this pair of models uses continuous measures of aid and debt as predictors. Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor). The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate. Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits. Zero is indicated along the x-axis via a vertical dashed line. If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.

@@

To put these estimates in more substantive terms, it will be helpful to show some computed marginal effects. Table \@ref(tab:mareff) shows the predicted change in each of the outcomes given a percent increase in either aid or debt. The estimates were computed for Pakistan in 2017. Cell entries in the first column denote the \% change in the number of times Pakistan appears in *Xinhua* in 2017 while entries in the second column denote the \% change in the number of times Pakistan hosts diplomatic missions from Beijing in 2017. The first row indicates what this change is per a hypothetical percent increase aid from China to Pakistan, and the second row indicates what this change is per a hypothetical percent increase in loans (debt) from China to Pakistan. The marginal effect for aid on coverage in this case is 0.76\% while the marginal effect for debt on visits is 0.05\%.

# Discussion and Conclusion

Our findings paint an interesting picture of how China's overseas financing relates to other kinds of foreign policy activities, speicifically its coverage of aid recipients targeted at foreign audiences and its bilateral diplomatic missions. To the extent that aid is associated with improving Beijing's image and fostering closer ties with recipients, we expect Beijing to complement its aid activities with both more coverage and more diplomatic visits.

At the same time that we expected to observe these relationships for Chinese aid, we expected to find weaker relationships between these outcomes and Chinese loans. China's application of debt has become a point of controversy because of its proposed links to Beijing's comercial interests. We therefore hypothesized that loans from China would be independent of coverage and visits.

Our finding only partially support our expectations. As expected, aid recipients receive disproportionate coverage in *Xinhua*. However, they are no more likely to receive more diplomatic missions from Beijing. Conversely, while debt owed to China does not lead to more coverage in *Xinhua*, it does correspond with more diplomatic visits. These more complicated findings warrant further explanation and research. At minimum, the links between debt and diplomatic activities suggests that Beijing's commercial interests cannot be divorced entirely from foreign policy. China appears to engage in efforts to build diplomatic ties disproportionately in debtor countries (rather than aid recipients). This finding deserves attention by future scholars to assess possible mechanisms that lead debt and diplomacy to complement each other.
